Dispersion distance and the matter distribution of the Universe in dispersion space

### 2015-06-04 writeup/dm_space_distortions.tex
footnotes.
end on positive note

However, the lack of a kernel simplifies tomography---the use of sources at
multiple redshifts to unmix spatial scales.
Lensing tomography is inexact because the kernel's shape depends on
the source redshift, thus re-weighting the line-of-sight integral.
In contrast, the integrand in the dispersion-space integral
term is completely independent of the limit of integration, meaning
contributions from different parts of the line-of-sight (and thus different
spatial scales) can be separated exactly. A detailed study of dispersion space
tomography is beyond the scope of this work.  To avoid our results being
sensitive to the hard-to-model small scales, we assume that the contribution to the
integral term from radial distances $\chi'' < 500\,{\rm Mpc}/h$ are well
measured by the correlations with these radial slices. We thus ignore
contributions to the integral term from below this distance and neglect the
information from these slices in our sensitivity measurements. The smallest
spatial scale that contributes to our plotted angular power spectra out to
$\ell=1000$ is thus $k=2\,h/{\rm Mpc}$.

@@

We have
shown in Figure~\ref{f:sensitivity}
that a survey detecting $10000$ fast radio bursts of cosmological
origin could detect the
clustering signal. This is in rough
approximation to what might be achieved in a modest amount of time by the Canadian Hydrogen Intensity
Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
Square Kilometer Array\footnote{\url{http://www.skatelescope.org/}},
or other upcoming wide-field telescopes.
Looking forward, dispersion-space
clustering could become a precision probe of large-scale structure should
observational factors turn out to be favourable compared to spectroscopic
surveys. The baryon acoustic oscillation feature can be clearly seen in
Figure~\ref{f:terms} in the cross term and both
local-term curves. It may also be possible to extract the BAO feature
from the integral
term using tomography.
This however requires that the contribution to dispersion from
the source's environment and host halo be small compared to the
contribution from the IGM.

>>>>

However, the lack of a kernel simplifies tomography---the use of sources at
multiple redshifts to unmix spatial scales.
Lensing tomography is inexact because the kernel's shape depends on
the source redshift, thus re-weighting the line-of-sight integral.
In contrast, the integrand in the dispersion-space integral
term is completely independent of the limit of integration, meaning
contributions from different parts of the line-of-sight (and thus different
spatial scales) can be separated exactly. We leave a study of the potential of dispersion space
tomography to future work.  To avoid our results being
sensitive to the hard-to-model small scales, we assume that the contribution to the
integral term from radial distances $\chi'' < 500\,{\rm Mpc}/h$ are well
measured by the correlations with these radial slices. We thus ignore
contributions to the integral term from below this distance and neglect the
information from these slices in our sensitivity measurements. The smallest
spatial scale that contributes to our plotted angular power spectra out to
$\ell=1000$ is thus $k=2\,h/{\rm Mpc}$.

@@

We have
shown in Figure~\ref{f:sensitivity}
that a survey detecting $10000$ fast radio bursts of cosmological
origin could detect the
clustering signal. This is in rough
approximation to what might be achieved in a modest amount of time by the Canadian Hydrogen Intensity
Mapping Experiment (CHIME)\footnote{\url{http://chime.phas.ubc.ca/}}, the
Square Kilometer Array\footnote{\url{http://www.skatelescope.org/}},
or other upcoming wide-field telescopes.
Looking forward, dispersion-space
clustering could become a precision probe of large-scale structure should
observational factors turn out to be favourable compared to spectroscopic
surveys. The baryon acoustic oscillation feature can be clearly seen in
Figure~\ref{f:terms} in the cross term and both
local-term curves. It may also be possible to extract the BAO feature
from the integral
term using tomography.
This however requires that the statistics of the contribution to dispersion from
the source's environment and host halo to be well understood or small compared to the
contribution from the line-of-sight.

Finally, we note that alone or by combination of dispersion-space data with redshift-space data on a subset of the population, independent redshift surveys of large-scale-structure, or gravitational lensing data could yield very powerful probes of cosmology.   Cosmological dispersion-space data could open a new window on to the structure of the Universe.
